si: code and prose exploring Spatial Interaction models

### 2022-04-15 README.qmd
Portable file names

```{r distance plot}
library(si)
od = si_to_od(origins = zones, destinations = zones, max_euclidean_distance = 5000)
gravity_model = function(od, beta) {
  od[["origin_all"]] * od[["destination_all"]] *
    exp(-beta * od[["distance_euclidean"]] / 1000)
} 
od_res = si_model(od, fun = gravity_model, beta = 0.3, var_p = origin_all)
plot(od_res$distance_euclidean, od_res$res)
```

>>>>

```{r distance}
library(si)
od = si_to_od(origins = zones, destinations = zones, max_euclidean_distance = 5000)
gravity_model = function(od, beta) {
  od[["origin_all"]] * od[["destination_all"]] *
    exp(-beta * od[["distance_euclidean"]] / 1000)
} 
od_res = si_model(od, fun = gravity_model, beta = 0.3, var_p = origin_all)
plot(od_res$distance_euclidean, od_res$res)
```
